Curating RNAseq data for mouse and \textit{Eimeria falciformis}

### 2016-04-08 additional_files/tex/cluster2_BP_Mm_7dpiUp.tex
Large changes in annotation script and lots of small adjustments in others (paths changed, typos, ggpair command adjustment... etc)

% latex table generated in R 3.2.3 by xtable 1.8-2 package
% Thu Mar 24 05:57:46 2016

@@

1 & GO:0002376 & immune system process & 1326 & 136 & 44.91 & 0.00 & 0.00 \\ 
  2 & GO:0006955 & immune response & 674 &  91 & 22.83 & 0.00 & 0.00 \\ 
  3 & GO:0045321 & leukocyte activation & 487 &  74 & 16.50 & 0.00 & 0.00 \\ 
  4 & GO:0001775 & cell activation & 557 &  79 & 18.87 & 0.00 & 0.00 \\ 
  5 & GO:0022610 & biological adhesion & 769 &  90 & 26.05 & 0.00 & 0.00 \\ 
  6 & GO:0044700 & single organism signaling & 2837 & 190 & 96.09 & 0.00 & 0.00 \\ 
  7 & GO:0007155 & cell adhesion & 762 &  89 & 25.81 & 0.00 & 0.00 \\ 
  8 & GO:0023052 & signaling & 2844 & 190 & 96.33 & 0.00 & 0.00 \\ 
  9 & GO:0001816 & cytokine production & 381 &  62 & 12.91 & 0.00 & 0.00 \\ 
  10 & GO:0007154 & cell communication & 2986 & 194 & 101.14 & 0.00 & 0.00 \\ 
  11 & GO:0007165 & signal transduction & 2643 & 180 & 89.52 & 0.00 & 0.00 \\ 
  12 & GO:0002684 & positive regulation of immune system pro... & 471 &  68 & 15.95 & 0.00 & 0.00 \\ 
  13 & GO:0007159 & leukocyte cell-cell adhesion & 317 &  55 & 10.74 & 0.00 & 0.00 \\ 
  14 & GO:0002682 & regulation of immune system process & 732 &  84 & 24.79 & 0.00 & 0.00 \\ 
  15 & GO:0046649 & lymphocyte activation & 412 &  62 & 13.96 & 0.00 & 0.00 \\ 
  16 & GO:0048518 & positive regulation of biological proces... & 3218 & 200 & 109.00 & 0.00 & 0.00 \\ 
  17 & GO:0050896 & response to stimulus & 4167 & 234 & 141.14 & 0.00 & 0.00 \\ 
  18 & GO:0051239 & regulation of multicellular organismal p... & 1493 & 124 & 50.57 & 0.00 & 0.00 \\ 
  19 & GO:0098602 & single organism cell adhesion & 498 &  67 & 16.87 & 0.00 & 0.00 \\ 
  20 & GO:0016337 & single organismal cell-cell adhesion & 458 &  64 & 15.51 & 0.00 & 0.00 \\ 
  21 & GO:0001817 & regulation of cytokine production & 334 &  54 & 11.31 & 0.00 & 0.00 \\ 
  22 & GO:0006954 & inflammatory response & 316 &  52 & 10.70 & 0.00 & 0.00 \\ 
  23 & GO:0034109 & homotypic cell-cell adhesion & 346 &  54 & 11.72 & 0.00 & 0.00 \\ 
  24 & GO:0098609 & cell-cell adhesion & 485 &  64 & 16.43 & 0.00 & 0.00 \\ 
  25 & GO:0006952 & defense response & 724 &  79 & 24.52 & 0.00 & 0.00 \\ 
  26 & GO:0070486 & leukocyte aggregation & 301 &  50 & 10.20 & 0.00 & 0.00 \\ 
  27 & GO:0051716 & cellular response to stimulus & 3508 & 204 & 118.82 & 0.00 & 0.00 \\ 
  28 & GO:0040011 & locomotion & 869 &  85 & 29.43 & 0.00 & 0.00 \\ 
  29 & GO:0030155 & regulation of cell adhesion & 397 &  55 & 13.45 & 0.00 & 0.00 \\ 
  30 & GO:0042110 & T cell activation & 292 &  47 & 9.89 & 0.00 & 0.00 \\ 
  31 & GO:0070489 & T cell aggregation & 292 &  47 & 9.89 & 0.00 & 0.00 \\ 
  32 & GO:0048522 & positive regulation of cellular process & 2886 & 177 & 97.75 & 0.00 & 0.00 \\ 
  33 & GO:0071593 & lymphocyte aggregation & 294 &  47 & 9.96 & 0.00 & 0.00 \\ 
  34 & GO:0048870 & cell motility & 750 &  77 & 25.40 & 0.00 & 0.00 \\ 
  35 & GO:0051674 & localization of cell & 750 &  77 & 25.40 & 0.00 & 0.00 \\ 
  36 & GO:0002694 & regulation of leukocyte activation & 288 &  46 & 9.76 & 0.00 & 0.00 \\ 
  37 & GO:0016477 & cell migration & 712 &  74 & 24.12 & 0.00 & 0.00 \\ 
  38 & GO:0050865 & regulation of cell activation & 306 &  47 & 10.36 & 0.00 & 0.00 \\ 
  39 & GO:0044707 & single-multicellular organism process & 3254 & 188 & 110.22 & 0.00 & 0.00 \\ 
  40 & GO:0048583 & regulation of response to stimulus & 2012 & 137 & 68.15 & 0.00 & 0.00 \\ 
  41 & GO:0050900 & leukocyte migration & 157 &  33 & 5.32 & 0.00 & 0.00 \\ 
  42 & GO:0002521 & leukocyte differentiation & 328 &  47 & 11.11 & 0.00 & 0.00 \\ 
  43 & GO:0032501 & multicellular organismal process & 3326 & 189 & 112.66 & 0.00 & 0.00 \\ 
  44 & GO:0065007 & biological regulation & 6019 & 280 & 203.87 & 0.00 & 0.00 \\ 
  45 & GO:0050794 & regulation of cellular process & 5444 & 262 & 184.40 & 0.00 & 0.00 \\ 
  46 & GO:0051249 & regulation of lymphocyte activation & 246 &  40 & 8.33 & 0.00 & 0.00 \\ 
  47 & GO:0002520 & immune system development & 593 &  63 & 20.09 & 0.00 & 0.00 \\ 
  48 & GO:0001819 & positive regulation of cytokine producti... & 222 &  37 & 7.52 & 0.00 & 0.00 \\ 
  49 & GO:0006928 & movement of cell or subcellular componen... & 947 &  82 & 32.08 & 0.00 & 0.00 \\ 
  50 & GO:0050789 & regulation of biological process & 5734 & 268 & 194.22 & 0.00 & 0.00 \\ 
  51 & GO:0051240 & positive regulation of multicellular org... & 856 &  77 & 28.99 & 0.00 & 0.00 \\ 
  52 & GO:0030098 & lymphocyte differentiation & 225 &  37 & 7.62 & 0.00 & 0.00 \\ 
  53 & GO:0022407 & regulation of cell-cell adhesion & 238 &  38 & 8.06 & 0.00 & 0.00 \\ 
  54 & GO:0048534 & hematopoietic or lymphoid organ developm... & 557 &  59 & 18.87 & 0.00 & 0.00 \\ 
  55 & GO:0048584 & positive regulation of response to stimu... & 1076 &  87 & 36.45 & 0.00 & 0.00 \\ 
  56 & GO:0050776 & regulation of immune response & 366 &  46 & 12.40 & 0.00 & 0.00 \\ 
  57 & GO:0007166 & cell surface receptor signaling pathway & 1252 &  95 & 42.41 & 0.00 & 0.00 \\ 
  58 & GO:0002250 & adaptive immune response & 217 &  35 & 7.35 & 0.00 & 0.00 \\ 
  59 & GO:0009605 & response to external stimulus & 1135 &  89 & 38.44 & 0.00 & 0.00 \\ 
  60 & GO:0046651 & lymphocyte proliferation & 172 &  31 & 5.83 & 0.00 & 0.00 \\ 
  61 & GO:0032943 & mononuclear cell proliferation & 174 &  31 & 5.89 & 0.00 & 0.00 \\ 
  62 & GO:0060326 & cell chemotaxis & 141 &  28 & 4.78 & 0.00 & 0.00 \\ 
  63 & GO:0045785 & positive regulation of cell adhesion & 226 &  35 & 7.65 & 0.00 & 0.00 \\ 
  64 & GO:0070887 & cellular response to chemical stimulus & 1258 &  94 & 42.61 & 0.00 & 0.00 \\ 
  65 & GO:0070661 & leukocyte proliferation & 178 &  31 & 6.03 & 0.00 & 0.00 \\ 
  66 & GO:0035556 & intracellular signal transduction & 1498 & 105 & 50.74 & 0.00 & 0.00 \\ 
  67 & GO:1903037 & regulation of leukocyte cell-cell adhesi... & 179 &  31 & 6.06 & 0.00 & 0.00 \\ 
  68 & GO:0008219 & cell death & 1318 &  96 & 44.64 & 0.00 & 0.00 \\ 
  69 & GO:0016265 & death & 1321 &  96 & 44.74 & 0.00 & 0.00 \\ 
  70 & GO:0030595 & leukocyte chemotaxis &  97 &  23 & 3.29 & 0.00 & 0.00 \\ 
  71 & GO:0050867 & positive regulation of cell activation & 184 &  31 & 6.23 & 0.00 & 0.00 \\ 
  72 & GO:0040017 & positive regulation of locomotion & 262 &  37 & 8.87 & 0.00 & 0.00 \\ 
  73 & GO:0097530 & granulocyte migration &  63 &  19 & 2.13 & 0.00 & 0.00 \\ 
  74 & GO:0022409 & positive regulation of cell-cell adhesio... & 129 &  26 & 4.37 & 0.00 & 0.00 \\ 
  75 & GO:0097529 & myeloid leukocyte migration &  90 &  22 & 3.05 & 0.00 & 0.00 \\ 
  76 & GO:0006935 & chemotaxis & 266 &  37 & 9.01 & 0.00 & 0.00 \\ 
  77 & GO:0030097 & hemopoiesis & 528 &  54 & 17.88 & 0.00 & 0.00 \\ 
  78 & GO:0042330 & taxis & 267 &  37 & 9.04 & 0.00 & 0.00 \\ 
  79 & GO:0002696 & positive regulation of leukocyte activat... & 179 &  30 & 6.06 & 0.00 & 0.00 \\ 
  80 & GO:0030335 & positive regulation of cell migration & 245 &  35 & 8.30 & 0.00 & 0.00 \\ 
  81 & GO:0010646 & regulation of cell communication & 1709 & 112 & 57.89 & 0.00 & 0.00 \\ 
  82 & GO:0050793 & regulation of developmental process & 1301 &  93 & 44.07 & 0.00 & 0.00 \\ 
  83 & GO:2000147 & positive regulation of cell motility & 250 &  35 & 8.47 & 0.00 & 0.00 \\ 
  84 & GO:0023051 & regulation of signaling & 1678 & 110 & 56.84 & 0.00 & 0.00 \\ 
  85 & GO:0002460 & adaptive immune response based on somati... & 150 &  27 & 5.08 & 0.00 & 0.00 \\ 
  86 & GO:0001818 & negative regulation of cytokine producti... & 128 &  25 & 4.34 & 0.00 & 0.00 \\ 
  87 & GO:0071621 & granulocyte chemotaxis &  54 &  17 & 1.83 & 0.00 & 0.00 \\ 
  88 & GO:0034110 & regulation of homotypic cell-cell adhesi... & 189 &  30 & 6.40 & 0.00 & 0.00 \\ 
  89 & GO:1990266 & neutrophil migration &  55 &  17 & 1.86 & 0.00 & 0.00 \\ 
  90 & GO:0051272 & positive regulation of cellular componen... & 257 &  35 & 8.70 & 0.00 & 0.00 \\ 
  91 & GO:1903039 & positive regulation of leukocyte cell-ce... & 110 &  23 & 3.73 & 0.00 & 0.00 \\ 
  92 & GO:0009966 & regulation of signal transduction & 1495 & 101 & 50.64 & 0.00 & 0.00 \\ 
  93 & GO:0042221 & response to chemical & 1780 & 113 & 60.29 & 0.00 & 0.00 \\ 
  94 & GO:0002443 & leukocyte mediated immunity & 196 &  30 & 6.64 & 0.00 & 0.00 \\ 
  95 & GO:0050863 & regulation of T cell activation & 172 &  28 & 5.83 & 0.00 & 0.00 \\ 
  96 & GO:0051270 & regulation of cellular component movemen... & 467 &  48 & 15.82 & 0.00 & 0.00 \\ 
  97 & GO:0044763 & single-organism cellular process & 6624 & 285 & 224.37 & 0.00 & 0.00 \\ 
  98 & GO:0006915 & apoptotic process & 1219 &  87 & 41.29 & 0.00 & 0.00 \\ 
  99 & GO:0012501 & programmed cell death & 1241 &  88 & 42.03 & 0.00 & 0.00 \\ 
  100 & GO:0002252 & immune effector process & 440 &  46 & 14.90 & 0.00 & 0.00 \\ 

>>>>

% latex table generated in R 3.2.2 by xtable 1.8-2 package
% Fri Apr  8 11:17:23 2016

@@

1 & GO:0055114 & oxidation-reduction process & 650 &  28 & 9.76 & 0.00 & 0.00 \\ 
  2 & GO:0044281 & small molecule metabolic process & 1261 &  42 & 18.94 & 0.00 & 0.00 \\ 
  3 & GO:0006629 & lipid metabolic process & 796 &  29 & 11.95 & 0.00 & 0.00 \\ 
  4 & GO:0044710 & single-organism metabolic process & 3313 &  76 & 49.76 & 0.00 & 0.00 \\ 
  5 & GO:0006805 & xenobiotic metabolic process &  42 &   6 & 0.63 & 0.00 & 0.00 \\ 
  6 & GO:0071466 & cellular response to xenobiotic stimulus &  46 &   6 & 0.69 & 0.00 & 0.00 \\ 
  7 & GO:0009410 & response to xenobiotic stimulus &  51 &   6 & 0.77 & 0.00 & 0.00 \\ 
  8 & GO:0006140 & regulation of nucleotide metabolic proce... & 103 &   8 & 1.55 & 0.00 & 0.00 \\ 
  9 & GO:1901387 & positive regulation of voltage-gated cal... &   2 &   2 & 0.03 & 0.00 & 0.00 \\ 
  10 & GO:0009117 & nucleotide metabolic process & 400 &  16 & 6.01 & 0.00 & 0.00 \\ 
  11 & GO:0017144 & drug metabolic process &  23 &   4 & 0.35 & 0.00 & 0.00 \\ 
  12 & GO:0019369 & arachidonic acid metabolic process &  24 &   4 & 0.36 & 0.00 & 0.00 \\ 
  13 & GO:0006753 & nucleoside phosphate metabolic process & 408 &  16 & 6.13 & 0.00 & 0.00 \\ 
  14 & GO:0008202 & steroid metabolic process & 169 &   9 & 2.54 & 0.00 & 0.01 \\ 
  15 & GO:0055086 & nucleobase-containing small molecule met... & 443 &  16 & 6.65 & 0.00 & 0.01 \\ 
  16 & GO:0015701 & bicarbonate transport &  14 &   3 & 0.21 & 0.00 & 0.01 \\ 
  17 & GO:0042738 & exogenous drug catabolic process &  14 &   3 & 0.21 & 0.00 & 0.01 \\ 
  18 & GO:0006631 & fatty acid metabolic process & 243 &  11 & 3.65 & 0.00 & 0.01 \\ 
  19 & GO:0051289 & protein homotetramerization &  53 &   5 & 0.80 & 0.00 & 0.01 \\ 
  20 & GO:0009992 & cellular water homeostasis &   4 &   2 & 0.06 & 0.00 & 0.01 \\ 
  21 & GO:0032782 & bile acid secretion &   4 &   2 & 0.06 & 0.00 & 0.01 \\ 
  22 & GO:0042737 & drug catabolic process &  15 &   3 & 0.23 & 0.00 & 0.01 \\ 
  23 & GO:0006690 & icosanoid metabolic process &  55 &   5 & 0.83 & 0.00 & 0.01 \\ 
  24 & GO:1901568 & fatty acid derivative metabolic process &  55 &   5 & 0.83 & 0.00 & 0.01 \\ 
  25 & GO:0015850 & organic hydroxy compound transport & 116 &   7 & 1.74 & 0.00 & 0.01 \\ 
  26 & GO:0043583 & ear development & 116 &   7 & 1.74 & 0.00 & 0.01 \\ 
  27 & GO:0051262 & protein tetramerization &  87 &   6 & 1.31 & 0.00 & 0.01 \\ 
  28 & GO:0055085 & transmembrane transport & 563 &  18 & 8.46 & 0.00 & 0.01 \\ 
  29 & GO:0045989 & positive regulation of striated muscle c... &   5 &   2 & 0.08 & 0.00 & 0.01 \\ 
  30 & GO:0042445 & hormone metabolic process &  89 &   6 & 1.34 & 0.00 & 0.01 \\ 
  31 & GO:0051186 & cofactor metabolic process & 265 &  11 & 3.98 & 0.00 & 0.01 \\ 
  32 & GO:0030104 & water homeostasis &  18 &   3 & 0.27 & 0.00 & 0.01 \\ 
  33 & GO:0071333 & cellular response to glucose stimulus &  62 &   5 & 0.93 & 0.00 & 0.01 \\ 
  34 & GO:0019637 & organophosphate metabolic process & 668 &  20 & 10.03 & 0.00 & 0.01 \\ 
  35 & GO:0046903 & secretion & 625 &  19 & 9.39 & 0.00 & 0.01 \\ 
  36 & GO:0071326 & cellular response to monosaccharide stim... &  64 &   5 & 0.96 & 0.00 & 0.01 \\ 
  37 & GO:0071331 & cellular response to hexose stimulus &  64 &   5 & 0.96 & 0.00 & 0.01 \\ 
  38 & GO:0019373 & epoxygenase P450 pathway &   6 &   2 & 0.09 & 0.00 & 0.01 \\ 
  39 & GO:0019532 & oxalate transport &   6 &   2 & 0.09 & 0.00 & 0.01 \\ 
  40 & GO:0048505 & regulation of timing of cell differentia... &   6 &   2 & 0.09 & 0.00 & 0.01 \\ 
  41 & GO:0071322 & cellular response to carbohydrate stimul... &  68 &   5 & 1.02 & 0.00 & 0.01 \\ 
  42 & GO:1900542 & regulation of purine nucleotide metaboli... &  98 &   6 & 1.47 & 0.00 & 0.01 \\ 
  43 & GO:0050433 & regulation of catecholamine secretion &  21 &   3 & 0.32 & 0.00 & 0.01 \\ 
  44 & GO:0015711 & organic anion transport & 207 &   9 & 3.11 & 0.00 & 0.01 \\ 
  45 & GO:0016042 & lipid catabolic process & 172 &   8 & 2.58 & 0.00 & 0.01 \\ 
  46 & GO:0003214 & cardiac left ventricle morphogenesis &   7 &   2 & 0.11 & 0.00 & 0.01 \\ 
  47 & GO:0006833 & water transport &   7 &   2 & 0.11 & 0.00 & 0.01 \\ 
  48 & GO:0032099 & negative regulation of appetite &   7 &   2 & 0.11 & 0.00 & 0.01 \\ 
  49 & GO:1902358 & sulfate transmembrane transport &   7 &   2 & 0.11 & 0.00 & 0.01 \\ 
  50 & GO:0001678 & cellular glucose homeostasis &  72 &   5 & 1.08 & 0.00 & 0.01 \\ 
  51 & GO:0032787 & monocarboxylic acid metabolic process & 377 &  13 & 5.66 & 0.00 & 0.01 \\ 
  52 & GO:0007200 & phospholipase C-activating G-protein cou... &  23 &   3 & 0.35 & 0.00 & 0.01 \\ 
  53 & GO:0050432 & catecholamine secretion &  23 &   3 & 0.35 & 0.00 & 0.01 \\ 
  54 & GO:0001676 & long-chain fatty acid metabolic process &  47 &   4 & 0.71 & 0.01 & 0.01 \\ 
  55 & GO:0032105 & negative regulation of response to extra... &  24 &   3 & 0.36 & 0.01 & 0.01 \\ 
  56 & GO:0032108 & negative regulation of response to nutri... &  24 &   3 & 0.36 & 0.01 & 0.01 \\ 
  57 & GO:0055082 & cellular chemical homeostasis & 342 &  12 & 5.14 & 0.01 & 0.01 \\ 
  58 & GO:0032612 & interleukin-1 production &  48 &   4 & 0.72 & 0.01 & 0.01 \\ 
  59 & GO:0006820 & anion transport & 302 &  11 & 4.54 & 0.01 & 0.01 \\ 
  60 & GO:0032096 & negative regulation of response to food &   8 &   2 & 0.12 & 0.01 & 0.01 \\ 
  61 & GO:0033604 & negative regulation of catecholamine sec... &   8 &   2 & 0.12 & 0.01 & 0.01 \\ 
  62 & GO:0040034 & regulation of development, heterochronic &   8 &   2 & 0.12 & 0.01 & 0.01 \\ 
  63 & GO:0060081 & membrane hyperpolarization &   8 &   2 & 0.12 & 0.01 & 0.01 \\ 
  64 & GO:0060979 & vasculogenesis involved in coronary vasc... &   8 &   2 & 0.12 & 0.01 & 0.01 \\ 
  65 & GO:0006730 & one-carbon metabolic process &  25 &   3 & 0.38 & 0.01 & 0.01 \\ 
  66 & GO:1901661 & quinone metabolic process &  25 &   3 & 0.38 & 0.01 & 0.01 \\ 
  67 & GO:1901135 & carbohydrate derivative metabolic proces... & 677 &  19 & 10.17 & 0.01 & 0.01 \\ 
  68 & GO:0034220 & ion transmembrane transport & 393 &  13 & 5.90 & 0.01 & 0.01 \\ 
  69 & GO:0030004 & cellular monovalent inorganic cation hom... &  50 &   4 & 0.75 & 0.01 & 0.01 \\ 
  70 & GO:0009187 & cyclic nucleotide metabolic process &  79 &   5 & 1.19 & 0.01 & 0.01 \\ 
  71 & GO:0010817 & regulation of hormone levels & 267 &  10 & 4.01 & 0.01 & 0.01 \\ 
  72 & GO:0008272 & sulfate transport &   9 &   2 & 0.14 & 0.01 & 0.01 \\ 
  73 & GO:0032148 & activation of protein kinase B activity &   9 &   2 & 0.14 & 0.01 & 0.01 \\ 
  74 & GO:0071875 & adrenergic receptor signaling pathway &   9 &   2 & 0.14 & 0.01 & 0.01 \\ 
  75 & GO:0052652 & cyclic purine nucleotide metabolic proce... &  52 &   4 & 0.78 & 0.01 & 0.01 \\ 
  76 & GO:0072521 & purine-containing compound metabolic pro... & 315 &  11 & 4.73 & 0.01 & 0.01 \\ 
  77 & GO:0009190 & cyclic nucleotide biosynthetic process &  53 &   4 & 0.80 & 0.01 & 0.01 \\ 
  78 & GO:0051937 & catecholamine transport &  28 &   3 & 0.42 & 0.01 & 0.01 \\ 
  79 & GO:0019318 & hexose metabolic process & 154 &   7 & 2.31 & 0.01 & 0.01 \\ 
  80 & GO:0045981 & positive regulation of nucleotide metabo... &  54 &   4 & 0.81 & 0.01 & 0.01 \\ 
  81 & GO:1900544 & positive regulation of purine nucleotide... &  54 &   4 & 0.81 & 0.01 & 0.01 \\ 
  82 & GO:0045980 & negative regulation of nucleotide metabo... &  29 &   3 & 0.44 & 0.01 & 0.01 \\ 
  83 & GO:0002275 & myeloid cell activation involved in immu... &  55 &   4 & 0.83 & 0.01 & 0.01 \\ 
  84 & GO:0032098 & regulation of appetite &  10 &   2 & 0.15 & 0.01 & 0.01 \\ 
  85 & GO:0051923 & sulfation &  10 &   2 & 0.15 & 0.01 & 0.01 \\ 
  86 & GO:0042493 & response to drug & 158 &   7 & 2.37 & 0.01 & 0.01 \\ 
